### 2017-01-14 chi/piecework/complexity.tex
fixed a few bugs: - fixed a citation on page 4 that handled citeyear incorrectly (and other citeyear and citeauthor issues) - fixed a very weird sudden line break on page 5 (h/t Ranjay for spotting it during a read through) - fixed a smaller spelling error (it'ss -> it's) on page 6 (also Ranjay)

But when piecework intially entered the American economy,
it was not used for complex work.
Without having designed complex work processes, piecework managers were restricted to available workers' skills such as sewing: it was infeasible to provide new pieceworkers with the comprehensive education
that apprenticeships imparted \cite{hart2013rise}.
So, initially piecework arose for farm work, and as

Raynbird and others discuss,
the practice remained relatively obscure until
it blossomed in the textile industry~\cite{hughRaynbirdTaskWork}.
Complexity levels remained low at the turn of
the \nth{20} century as piecework saturated densely populated urban areas
such as London and New York City~\cite{riisOtherSideLives}.

@@

So, in the case of complexity, the history of piecework does not yet offer compelling evidence that on--demand work will achieve far more complex outcomes than piecework did.
Improvements in workflows, measurement, and evaluation have already been made, and it'ss not immediately clear that the remaining challenges are readily solvable.
However, on--demand work will be far more broadly distributed than piecework historically was
--- reaching many more tasks and areas of expertise by virtue of the internet.

>>>>

But when piecework intially entered the American economy,
it was not used for complex work.
Without having designed complex work processes, piecework managers were restricted to available workers' skills such as sewing: it was infeasible to provide new pieceworkers with the comprehensive education
that apprenticeships imparted \cite{hart2013rise}.
So, initially piecework arose for farm work, and as
Raynbird and others discuss,
the practice remained relatively obscure until
it blossomed in the textile industry~\cite{hughRaynbirdTaskWork}.
Complexity levels remained low at the turn of
the \nth{20} century as piecework saturated densely populated urban areas
such as London and New York City~\cite{riisOtherSideLives}.

@@

So, in the case of complexity, the history of piecework does not yet offer compelling evidence that on--demand work will achieve far more complex outcomes than piecework did.
Improvements in workflows, measurement, and evaluation have already been made, and it's not immediately clear that the remaining challenges are readily solvable.
However, on--demand work will be far more broadly distributed than piecework historically was
--- reaching many more tasks and areas of expertise by virtue of the internet.

### 2017-01-14 chi/piecework/relationships.tex
fixed a few bugs: - fixed a citation on page 4 that handled citeyear incorrectly (and other citeyear and citeauthor issues) - fixed a very weird sudden line break on page 5 (h/t Ranjay for spotting it during a read through) - fixed a smaller spelling error (it'ss -> it's) on page 6 (also Ranjay)

\topic{The relationship between workers and employers has also shifted: while historically the management of workers had to be done through a foreman,
% (who necessarily had an intuitive
% --- perhaps sympathetic ---
% relationship with workers),
foremen of the \nth{20} century have largely been replaced
by algorithms of the \nth{21} century~\cite{uberAlgorithm}.}
% The result of this change is that
Consequently,
the agents managing work are now
cold, logical, and unforgiving.
While a person might recognize that the ``attention check'' questions
proposed by Le et al. and others ensure that
malicious and inattentive workers are stopped~\cite{le2010ensuring,AAAIW113995},
some implementations of these approaches
only seem to antagonize workers~\cite{takingAHITMcInnis}.
As Anderson and Schmittlein wrote in \citeyear{10.2307/2555446},
``when performance is difficult to evaluate,
imperfect input measures and
a manager's subjective judgment are preferable to
defective (simple, observable) output measures''~\cite{10.2307/2555446}.
This frustration has only grown as requesters have had to rely on automatic management mechanisms.
Only a few use the equivalent of human foremen~\cite{haas2015argonaut,kulkarni2012mobileworks}.

>>>>

\topic{The relationship between workers and employers has also shifted: while historically the management of workers had to be done through a foreman,
% (who necessarily had an intuitive
% --- perhaps sympathetic ---
% relationship with workers),
foremen of the \nth{20} century have largely been replaced
by algorithms of the \nth{21} century~\cite{uberAlgorithm}.}
% The result of this change is that
Consequently,
the agents managing work are now
cold, logical, and unforgiving.
While a person might recognize that the ``attention check'' questions
proposed by Le et al. and others ensure that
malicious and inattentive workers are stopped~\cite{le2010ensuring,AAAIW113995},
some implementations of these approaches
only seem to antagonize workers~\cite{takingAHITMcInnis}.
As Anderson and Schmittlein wrote in 1984,
``when performance is difficult to evaluate,
imperfect input measures and
a manager's subjective judgment are preferable to
defective (simple, observable) output measures''~\cite{10.2307/2555446}.
This frustration has only grown as requesters have had to rely on automatic management mechanisms.
Only a few use the equivalent of human foremen~\cite{haas2015argonaut,kulkarni2012mobileworks}.

### 2017-01-14 drafts/aggregator/introduction.tex
fixed a few bugs: - fixed a citation on page 4 that handled citeyear incorrectly (and other citeyear and citeauthor issues) - fixed a very weird sudden line break on page 5 (h/t Ranjay for spotting it during a read through) - fixed a smaller spelling error (it'ss -> it's) on page 6 (also Ranjay)

Online labor markets ranging a variety of industries of (largely) service work
--- e.g. on--demand drivers (Uber, Lyft, Sidecar, etc\dots) and
    information work (Amazon Mechanical Turk, Upwork, CrowdFlower, etc\dots) ---
have struggled for some time with pernicious, in some cases \textit{growing},
difficulty assessing the quality of its workforce,
especially as it applies to a given task.
In other words, whether a worker on Amazon Mechanical Turk (AMT) is likely
to complete a task ``accurately'' remains an open question,
leading researchers to address this pervasive problem in a number of ways
\cite

@@

\onlyinsubfile{
% \balance{}
\printbibliography{}
}

>>>>

On--demand work has so far been a compelling way to arrange work and imagine workers;
the fleeting nature of work seems to appeal greatly to workers, and
the looser expectations of responsibility toward workers appeals to employers and clients.
But in the exchange we've made for more fleeting relationships,
we've instantiated --- or at least added fuel to ---
another class of challenges and problems.
Among them remains the challenge of ensuring that workers
--- first crowd workers, and later gig workers --- both
\begin{inlinelist}
\item know the skills necessary to do the immediate task and
\item will continue to produce work at the desired level of quality.
\end{inlinelist}
By far, two approaches have taken hold:
First, qualification exams (e.g. Amazon Mechanical Turk and Upwork),
       which ask workers to take a test of some sort to demonstrate that they both
       understand the task in question \textit{have the ability} to do the task.
Second, relying on outside certification bodies (e.g. Uber, \ali{do we know of others that match this profile?}),
        which assumes that outside bodies
        --- in Uber's case, local DMVs and similar bodies ---
        have sufficiently evaluated a person's ability to do the tasks necessary.

Other approaches exist, but have not (yet) garnered the interest of on--demand firms in general.

% Research has looked into this question from a handful of perspectives;
% some have tackled the qualifications problem as a pure assessment problem.
% others have looked to
% [\textit{Krishna et al. on long--term workers}]

\ali{I want citations on \textbf{worker qualifications} and on \textbf{worker effort and management}.
I think Ranjay's paper on looking forward etc\dots~at CSCW 2017 would be right here.
When do bibtex things come out?}

% Online labor markets ranging a variety of industries of (largely) service work
% --- e.g. on--demand drivers (Uber, Lyft, Sidecar, etc\dots) and
%     information work (Amazon Mechanical Turk, Upwork, CrowdFlower, etc\dots) ---
% have struggled for some time with pernicious, in some cases \textit{growing},
% difficulty assessing the quality of its workforce,
% especially as it applies to a given task.
% In other words, whether a worker on Amazon Mechanical Turk (AMT) is likely
% to complete a task ``accurately'' remains an open question,
% leading researchers to address this pervasive problem in a number of ways

@@
